The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-08 paper/sections/results.tex

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/scalability.pdf}
  \caption{\revise{Here we progressively add more degrees of freedom to a beam by iteratively inserting 4 part sections, extending the beam in the $x$-axis direction at each step. On the left we report the number of non-zeros as a percentage of the total number of elements in the stiffness matrix (nnz$\%$)}. The right plot shows the average runtime of a simulation step as the number of degrees of freedom increases.}
  \label{fig:scalability}
\end{figure}

We also show that our raycasting weight computation is able to create shape-aware output. \reffig{independence} shows that manipulating
parts that are nearby but separated will behave in an appropriately independent fashion. Our grumpy model is capable of extending 
its leg without causing unrealistic deformations in the plant foot.

@@

@@

%show stoppers
Finally we show a few additional examples, highlighting the ability of SEM to handle complex simulations involving deformation, contact and friction.
In \reffig{staypuft} we show two astronauts in jaunty space suits collide in zero gravity. 
SEM gracefully allows bounded discontinuities in simulation output to allow for rich motion. 
This is similar to Discontinous Galerkin approaches but in SEM this behavior emerges from the kinematic model, rather than from additional flux terms~\cite{kaufmann2009flexible}.
\revise{Our soft enforcement of part connectivity at boundaries is a result of weighting function attributing equal weight values to equidistant parts. This equal weighting induces elastic forces that attempt to enforce continuity. In our examples this only introduces minor artifacts affecting the rendering, but this may be addressed using a separate rendering mesh or by using a representation with explicit connectivity.}
\revise{In \reffig{octopus} we demonstrate the shape-aware nature of our algorithm on a  stable Neo-Hookean ~\cite{SNHkim} simulation of an octopus, and observe independent motion for each limb.}

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/octopus.pdf}
  \caption{\revise{As a more extreme example of the shape-aware property of our algorithm, we simulate a falling octopus, and observe the 8 limbs moving independently. Self-collision is not accounted for here.}}
  \label{fig:octopus}
\end{figure}

>>>>

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/scalability.pdf}
  \caption{\revise{Here we progressively add more degrees of freedom to a beam by iteratively inserting 4 part sections, extending the beam in the $x$-axis direction at each step. On the left we report the number of non-zeros as a percentage of the total number of elements in the stiffness matrix (nnz$\%$). The right plot shows the average runtime of a simulation step as the number of degrees of freedom increases.}}
  \label{fig:scalability}
\end{figure}

We also show that our raycasting weight computation is able to create shape-aware output. \reffig{independence} and \reffig{octopus} show that manipulating
parts that are nearby but separated will behave in an appropriately independent fashion. Our grumpy model is capable of extending 
its leg without causing unrealistic deformations in the plant foot, and our octopus model shows independent motion of all eight limbs upon contact with the ground.

@@

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/octopus.pdf}
  \caption{\revise{We simulate a falling octopus, and observe the 8 limbs moving independently. Self-collision is not accounted for here.}}
  \label{fig:octopus}
\end{figure}

@@

%show stoppers
Finally we show a few additional examples, highlighting the ability of SEM to handle complex simulations involving deformation, contact and friction.
In \reffig{staypuft} we show two astronauts in jaunty space suits collide in zero gravity. 
SEM gracefully allows bounded discontinuities in simulation output to allow for rich motion. 
This is similar to Discontinous Galerkin approaches but in SEM this behavior emerges from the kinematic model, rather than from additional flux terms~\cite{kaufmann2009flexible}.
\revise{Our soft enforcement of part connectivity at boundaries is a result of weighting function attributing equal weight values to equidistant parts. This equal weighting induces elastic forces that attempt to enforce continuity. In our examples this only introduces minor artifacts affecting the rendering, but this may be addressed using a separate rendering mesh or by using a representation with explicit connectivity.}
